Welcome Home --- Now Vote!

### 2020-07-06 markdown/part2/supplemental.tex
commit july 6

\begin{singlespace}

\input{"../../temp/table55.tex"}
\end{singlespace}

@@

\begin{singlespace}
\input{"../../temp/iv_clean_reg.tex"}
\end{singlespace}

@@

\begin{singlespace}
\input{"../../temp/iv_clean_race_reg.tex"}
\end{singlespace}

@@

\begin{singlespace}
\input{"../../temp/iv_clean_months_reg.tex"}
\end{singlespace}

>>>>

\begin{singlespace}
\begin{table}[H] \centering
\fontsize{10}{12}\selectfont
\caption{\label{tab:to-16-logit} Individual-Level Logit Model}
\label{}
\begin{tabular}{@{\extracolsep{5pt}}lccc}
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{3}{c}{Cast Ballot in 2016 Election} \\
\\[-1.8ex] & (1) & (2) & (3)\\
\hline \\[-1.8ex]
D(Discharged on or after May 18\textsuperscript{th}, 2016) & $-$0.121 & $-$0.093 & $-$0.103 \\
& (0.093) & (0.094) & (0.094) \\
& & & \\
D(Male) &  & $-$0.490$^{***}$ & $-$0.524$^{***}$ \\
&  & (0.117) & (0.118) \\
& & & \\
Age (Years) &  & 0.034$^{***}$ & 0.030$^{***}$ \\
&  & (0.003) & (0.003) \\
& & & \\
Counts in Most Recent Sentence &  &  & 0.049$^{***}$ \\
&  &  & (0.014) \\
& & & \\
Time Spent on Parole (Years) & $-$3.105$^{***}$ & $-$4.354$^{***}$ & $-$4.264$^{***}$ \\
& (0.044) & (0.498) & (0.502) \\
& & & \\
\hline \\[-1.8ex]
Race / Ethnicity FE &  & X & X \\
Felony Class FE &  &  & X \\
\hline \\[-1.8ex]
Observations & 16,867 & 16,867 & 16,867 \\
Log Likelihood & $-$2,927.513 & $-$2,846.416 & $-$2,829.391 \\
Akaike Inf. Crit. & 5,859.027 & 5,712.831 & 5,690.782 \\
\hline \\[-1.8ex]
\multicolumn{4}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$. \\Robust standard errors in parentheses.}}}
\end{tabular}
\end{table}

\end{singlespace}

@@

\begin{singlespace}
\begin{table}[H]
\caption{\label{tab:iv-models-chunk}\label{tab:iv-models} Rights Restoration and Registration}
\fontsize{10}{12}\selectfont
\centering

\begin{tabular}{lccccc}
\\[-1.8ex]\hline
& \multicolumn{5}{c}{Registered to Vote} \\
& \multicolumn{2}{c}{2SLS} & \multicolumn{1}{c}{2S Probit} &   \multicolumn{2}{c}{Bivariate Probit}\\
& & & \multicolumn{1}{c}{(Marg. Effects)} &   \multicolumn{2}{c}{(Marg. Effects)}\\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-6}
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5)\\
\hline
D(Rights Restored) & 0.0137** & 0.0164*** & 0.0253*** & 0.0125** & 0.0157*** \\
 & (0.0058) & (0.0058) & (0.0055) & (0.0051) & (0.0051) \\
D(Male) &  & -0.0295*** & -0.0268*** &  & -0.0269*** \\
 &  & (0.0067) & (0.0054) &  & (0.0054) \\
Age (Years) &  & 0.0013*** & 0.0013*** &  & 0.0013*** \\
 &  & (0.0002) & (0.0001) &  & (0.0001) \\
Years on Parole &  & -0.0000 & -0.0000 &  & -0.0001 \\
 &  & (0.0009) & (0.0008) &  & (0.0008) \\
Constant & 0.0545*** & -0.0053 &  &  &  \\
 & (0.0019) & (0.0151) &  &  &  \\
\hline
Race / Ethnicity FE &  & X & X &  & X \\
Felony Class FE &  & X & X &  & X \\
\hline
Observations & 18,423 & 18,423 & 18,423 & 18,423 & 18,423 \\
Adjusted R$^2$ & 0.0008 & 0.0113 &  &  &  \\
Wald $\chi^2$ &  &  & 214.6 & 1171 & 1581 \\
 $\rho$ &  &  &  & 0.0855 & 0.0452 \\
\hline
\multicolumn{3}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$. \\
Robust standard errors in parentheses. \\
Instrument is dummy indicating whether \\
individual discharged after EO 181 went into effect. \\
First-stage equations include covariates in Models 2 -- 3. \\
Models 3 -- 5 present marginal effects, not model coefficients.}}}
\end{tabular}
\end{table}

\end{singlespace}

@@

\begin{singlespace}
\begin{table}[H]
\caption{\label{tab:iv-models-r-chunk}\label{tab:iv-models-r} Rights Restoration and Registration}
\fontsize{10}{12}\selectfont
\centering

\begin{tabular}{lcccccc}
\\[-1.8ex]\hline
& \multicolumn{6}{c}{Registered to Vote} \\
& \multicolumn{3}{c}{2SLS} &  \multicolumn{3}{c}{Bivariate Probit}\\
& & & &   \multicolumn{3}{c}{(Marg. Effects)}\\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
\\[-1.8ex] & White & Non-White & Black& White & Non-White & Black\\
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
\hline
D(Rights Restored) & 0.0235*** & 0.0114 & 0.0030 & 0.0225*** & 0.0109* & 0.0039 \\
 & (0.0090) & (0.0075) & (0.0093) & (0.0087) & (0.0063) & (0.0084) \\
D(Male) & -0.0099 & -0.0523*** & -0.0581*** & -0.0093 & -0.0424*** & -0.0479*** \\
 & (0.0078) & (0.0112) & (0.0146) & (0.0073) & (0.0074) & (0.0101) \\
Age (Years) & 0.0021*** & 0.0010*** & 0.0008*** & 0.0018*** & 0.0010*** & 0.0008*** \\
 & (0.0003) & (0.0002) & (0.0003) & (0.0002) & (0.0002) & (0.0003) \\
Years on Parole & 0.0019 & -0.0010 & 0.0018 & 0.0014 & -0.0010 & 0.0016 \\
 & (0.0022) & (0.0010) & (0.0016) & (0.0017) & (0.0010) & (0.0015) \\
Constant & -0.0417*** & 0.0688*** & 0.0834*** &  &  &  \\
 & (0.0150) & (0.0146) & (0.0197) &  &  &  \\
\hline
Felony Class FE & X & X & X & X & X & X \\
\hline
Observations & 5,691 & 12,732 & 7,843 & 5,691 & 12,732 & 7,843 \\
Adjusted R$^2$ & 0.0172 & 0.0066 & 0.0073 &  &  &  \\
Wald $\chi^2$ &  &  &  & 408.1 & 1163 & 923.7 \\
 $\rho$ &  &  &  & -0.135 & 0.150 & 0.153 \\
\hline
\multicolumn{3}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$. \\
Robust standard errors in parentheses. \\
Instrument is dummy indicating whether \\
individual discharged after EO 181 went into effect. \\
First-stage equations include covariates in all models. \\
Models 4 -- 6 present marginal effects, not model coefficients.}}}
\end{tabular}
\end{table}

\end{singlespace}

@@

\begin{singlespace}
\begin{table}[H]
\caption{\label{tab:iv-models-chunk-time}\label{tab:iv-models-time} Rights Restoration and Registration}
\fontsize{10}{12}\selectfont
\centering

\begin{tabular}{lcc}
\\[-1.8ex]\hline
& \multicolumn{2}{c}{Registered to Vote} \\
& \multicolumn{1}{c}{2SLS} & \multicolumn{1}{c}{2S Probit}\\
& &  \multicolumn{1}{c}{(Marg. Effects)}\\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3}
\\[-1.8ex] & (1) & (2) \\
\hline
Months Restored & 0.0052*** & 0.0088*** \\
 & (0.0018) & (0.0016) \\
D(Male) & -0.0295*** & -0.0267*** \\
 & (0.0067) & (0.0054) \\
Age (Years) & 0.0013*** & 0.0013*** \\
 & (0.0002) & (0.0001) \\
Years on Parole & -0.0000 & -0.0000 \\
 & (0.0009) & (0.0008) \\
Constant & -0.0058 &  \\
 & (0.0151) &  \\
\hline
Race / Ethnicity FE & X & X \\
Felony Class FE & X & X \\
\hline
Observations & 18,423 & 18,423 \\
Adjusted R$^2$ & 0.0115 &  \\
 Wald $\chi^2$ &  & 213.6 \\
\hline
\multicolumn{3}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$. \\
Robust standard errors in parentheses. \\
Instrument is dummy indicating whether \\
individual discharged after EO 181 went into effect. \\
First-stage equations include covariates in both models. \\
Model 2 presents marginal effects, not model coefficients.}}}
\end{tabular}
\end{table}

\end{singlespace}

### 2020-07-06 presentations/mpsa.tex
commit july 6

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usetheme[]{Berlin}
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Felony Disenfranchisement and Neighborhood Turnout},
  pdfauthor={Kevin Morris},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{Felony Disenfranchisement and Neighborhood Turnout}
\subtitle{The Case of New York City}
\author{Kevin Morris}
\date{Southern Political Science Association, 2020}
\institute{Brennan Center for Justice}

@@

\begin{frame}{Outline}
\protect\hypertarget{outline}{}
\begin{itemize}[<+->]
\tightlist
\item
  Introducing space into the conversation
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Redefining ``lost voters''
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Identifying neighborhoods with lost voters
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Testing turnout effects
\end{itemize}
\end{frame}

\begin{frame}{Introducing Space}
\protect\hypertarget{introducing-space}{}
\begin{itemize}[<+->]
\tightlist
\item
  Most of the existing literature on felony disenfranchisement and
  indirect turnout effects looks for effects at the state level (Miles
  2004; Bowers and Preuhs 2009; King and Erickson 2016)
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  But we \emph{know} that incarceration patterns aren't uniformly
  distributed throughout a given state (see, for instance, Gelman,
  Fagan, and Kiss 2007)
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Turnout effects are likely to be socially mediated - and therefore
  show up in the neighborhoods where disenfranchised individuals live
  (e.g.~Foladare 1968; Huckfeldt 1979; Cho, Gimpel, and Dyck 2006)
\end{itemize}
\end{frame}

\begin{frame}{Redefining Lost Voters}
\protect\hypertarget{redefining-lost-voters}{}
\begin{itemize}[<+->]
\tightlist
\item
  Much of the existing literature cannot identify individuals who
  \emph{would have voted} if not for their disenfranchisement (Burch
  2013)
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  This undermines our ability to distinguish the causal effects of
  incarceration / probation from the effects of disenfranchisement
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  This is especially likely given the low turnout propensity among the
  formerly disenfranchised (e.g.~Meredith and Morse 2015; Gerber et al.
  2017; White 2019)
\end{itemize}
\end{frame}

\begin{frame}{This Project Addresses Both Problems}
\protect\hypertarget{this-project-addresses-both-problems}{}
\begin{itemize}[<+->]
\tightlist
\item
  Administrative data from the NYS DOC allows us to conduct
  individual-level analysis
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Purge records in the NYS voter file allow us to construct vote
  histories for disenfranchised individuals
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Lost voters are all formally disenfranchised individuals who have
  voted in the past 10 years
\end{itemize}
\end{frame}

\begin{frame}{Identifying Neighborhoods with Lost Voters}
\protect\hypertarget{identifying-neighborhoods-with-lost-voters}{}
\includegraphics[width=1\linewidth]{../temp/lost_voters_map}
\end{frame}

\begin{frame}{Methodology}
\protect\hypertarget{methodology}{}
\begin{itemize}
\item
  A genetic match algorithm (Sekhon 2011) is used to match treated
  census block groups to untreated ones.
\item
  Each block group is matched to 30 untreated block groups; matches are
  done with replacement.
\end{itemize}
\end{frame}

\begin{frame}{Matching Results}
\protect\hypertarget{matching-results}{}
\begin{center}\includegraphics[width=0.49\linewidth,height=0.49\textheight]{../temp/perc_white_spsa} \includegraphics[width=0.49\linewidth,height=0.49\textheight]{../temp/perc_black_spsa} \end{center}
\end{frame}

\begin{frame}{Matching Results}
\protect\hypertarget{matching-results-1}{}
\begin{center}\includegraphics[width=0.49\linewidth,height=0.49\textheight]{../temp/perc_latino_spsa} \includegraphics[width=0.49\linewidth,height=0.49\textheight]{../temp/income_spsa} \end{center}
\end{frame}

\begin{frame}{Testing Turnout Effects}
\protect\hypertarget{testing-turnout-effects}{}
\begin{center}\includegraphics[width=0.85\linewidth,height=0.85\textheight]{../temp/coef_plot1} \end{center}
\end{frame}

\begin{frame}{Testing Turnout Effects}
\protect\hypertarget{testing-turnout-effects-1}{}
\begin{center}\includegraphics[width=0.85\linewidth,height=0.85\textheight]{../temp/coef_plot2} \end{center}
\end{frame}

\begin{frame}{Testing Turnout Effects}
\protect\hypertarget{testing-turnout-effects-2}{}
\begin{center}\includegraphics[width=0.85\linewidth,height=0.85\textheight]{../temp/coef_plot3b} \end{center}
\end{frame}

\begin{frame}{Testing Turnout Effects}
\protect\hypertarget{testing-turnout-effects-3}{}
\includegraphics[width=1\linewidth]{../output/dep_map}
\end{frame}

\begin{frame}{Conclusions}
\protect\hypertarget{conclusions}{}
\begin{itemize}[<+->]
\tightlist
\item
  The indirect turnout effects identified in past research appear to be
  geographically concentrated where the lost voters live.
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Hajnal (2009) and others have demonstrated that turnout differentials
  can have real political implications, especially in low-turnout
  contests.
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Felony disenfranchisement undermines Black political representation at
  the local level.
\end{itemize}
\end{frame}

@@

\begin{frame}[allowframebreaks,allowframebreaks]{References}
\protect\hypertarget{references}{}
\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-Bowers2009}{}%
Bowers, Melanie, and Robert R. Preuhs. 2009. ``Collateral Consequences
of a Collateral Penalty: The Negative Effect of Felon Disenfranchisement
Laws on the Political Participation of Nonfelons.'' \emph{Social Science
Quarterly} 90 (3): 722--43.
\url{https://doi.org/10.1111/j.1540-6237.2009.00640.x}.

\leavevmode\hypertarget{ref-Burch2013}{}%
Burch, Traci. 2013. ``Effects of Imprisonment and Community Supervision
on Neighborhood Political Participation in North Carolina.'' Edited by
Christopher Wildeman, Jacob S. Hacker, and Vesla M. Weaver. \emph{The
ANNALS of the American Academy of Political and Social Science} 651 (1):
184--201. \url{https://doi.org/10.1177/0002716213503093}.

\leavevmode\hypertarget{ref-Cho2006}{}%
Cho, Wendy K. Tam, James G. Gimpel, and Joshua J. Dyck. 2006.
``Residential Concentration, Political Socialization, and Voter
Turnout.'' \emph{The Journal of Politics} 68 (1): 156--67.
\url{https://doi.org/10.1111/j.1468-2508.2006.00377.x}.

\leavevmode\hypertarget{ref-Foladare1968}{}%
Foladare, Irving S. 1968. ``The Effect of Neighborhood on Voting
Behavior.'' \emph{Political Science Quarterly} 83 (4): 516.
\url{https://doi.org/10.2307/2146812}.

\leavevmode\hypertarget{ref-Gelman2007}{}%
Gelman, Andrew, Jeffrey Fagan, and Alex Kiss. 2007. ``An Analysis of the
New York City Police Departments ``Stop-and-Frisk'' Policy in the
Context of Claims of Racial Bias.'' \emph{Journal of the American
Statistical Association} 102 (479): 813--23.
\url{https://doi.org/10.1198/016214506000001040}.

\leavevmode\hypertarget{ref-Gerber2017}{}%
Gerber, Alan S., Gregory A. Huber, Marc Meredith, Daniel R. Biggers, and
David J. Hendry. 2017. ``Does Incarceration Reduce Voting? Evidence
About the Political Consequences of Spending Time in Prison.'' \emph{The
Journal of Politics} 79 (4): 1130--46.
\url{https://doi.org/10.1086/692670}.

\leavevmode\hypertarget{ref-Hajnal2009}{}%
Hajnal, Zoltan. 2009. \emph{America's Uneven Democracy}. Cambridge
University Press. \url{https://doi.org/10.1017/cbo9780511800535}.

\leavevmode\hypertarget{ref-Huckfeldt1979}{}%
Huckfeldt, R. Robert. 1979. ``Political Participation and the
Neighborhood Social Context.'' \emph{American Journal of Political
Science} 23 (3): 579. \url{https://doi.org/10.2307/2111030}.

\leavevmode\hypertarget{ref-King2016}{}%
King, Bridgett A., and Laura Erickson. 2016. ``Disenfranchising the
Enfranchised.'' \emph{Journal of Black Studies} 47 (8): 799--821.
\url{https://doi.org/10.1177/0021934716659195}.

@@

\leavevmode\hypertarget{ref-Miles2004}{}%
Miles, Thomas J. 2004. ``Felon Disenfranchisement and Voter Turnout.''
\emph{The Journal of Legal Studies} 33 (1): 85--129.
\url{https://doi.org/10.1086/381290}.

\leavevmode\hypertarget{ref-Sekhon2011}{}%
Sekhon, Jasjeet S. 2011. ``Multivariate and Propensity Score Matching
Software with Automated Balance Optimization: The Matching Package for
R.'' \emph{Journal of Statistical Software} 42 (7).
\url{https://doi.org/10.18637/jss.v042.i07}.

\leavevmode\hypertarget{ref-White2019}{}%
White, Ariel. 2019. ``Misdemeanor Disenfranchisement? The Demobilizing
Effects of Brief Jail Spells on Potential Voters.'' \emph{American
Political Science Review} 113 (2): 311--24.
\url{https://doi.org/10.1017/s000305541800093x}.
\end{cslreferences}
\end{frame}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usetheme[]{Berlin}
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Welcome Home --- Now Vote!},
  pdfauthor={Kevin Morris},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{Welcome Home --- Now Vote!}
\subtitle{Voting Rights Restoration and Post-Supervision Turnout}
\author{Kevin Morris}
\date{Midwest Political Science Association, 2020}
\institute{Brennan Center for Justice}

@@

\begin{frame}{Outline}
\protect\hypertarget{outline}{}
\begin{itemize}[<+->]
\tightlist
\item
  Previous research indicates that notification laws increase
  post-supervision turnout
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  The notification laws are ``baked in'' to the control group here. In
  2018, New York State began implementing rights restoration prior to
  parole discharge at in-person meetings.
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  So --- did rights restoration \emph{prior} to parole discharge
  increase formerly incarcerated individuals' propensity to vote?
\end{itemize}
\end{frame}

\begin{frame}{Formerly Incarcerated Individuals Turn Out at Low Rates}
\protect\hypertarget{formerly-incarcerated-individuals-turn-out-at-low-rates}{}
\begin{itemize}[<+->]
\tightlist
\item
  The low turnout rates among the formerly disenfranchised have been
  shown in a number of studies (e.g.~Burch 2011, 2012; White 2019)
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  The \emph{causal effect} of incarceration, however, is the subject of
  some debate. Gerber et al. (2017), for instance, argues that most of
  the low turnout observed in the formerly incarcerated population is
  attributable not to incarceration, but to other factors predating
  incarceration.
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Nevertheless, Lerman and Weaver (2014) and others have convincingly
  shown through qualitative and quantitative work that criminal justice
  involvement structures individuals' relationship to the state.
\end{itemize}
\end{frame}

\begin{frame}{Notification Laws and Post-Supervision Turnout}
\protect\hypertarget{notification-laws-and-post-supervision-turnout}{}
\begin{itemize}[<+->]
\tightlist
\item
  In 2005, Iowa changed its disenfranchisement laws to allow formerly
  incarcerated individuals to vote. Not all formerly incarcerated
  individuals, however, were notified of the change in the mail.
  Meredith and Morse (2015) exploits this uneven treatment,
  demonstrating that mail notification increased turnout.
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  In 2012, Gerber et al. (2015) expanded on the natural experiment setup
  of Meredith and Morse (2015). In a randomized experiment, they sent
  mail notifications to some formerly disenfranchised individuals in
  Connecticut. They too find that notification increases participation,
  arguing ``Whatever the participatory consequences of incarceration
  they are not in large part impossible to overcome'' (p.~924).
\end{itemize}
\end{frame}

\begin{frame}{Changes in New York State in 2018}
\protect\hypertarget{changes-in-new-york-state-in-2018}{}
\begin{itemize}[<+->]
\tightlist
\item
  In the spring of 2018, Governor Andrew Cuomo signs Executive Order 181
  restoring voting rights to individuals \emph{prior} to their discharge
  from parole.
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  The New York DOC issues guidance calling the program a \emph{priority}
  initiative, telling parole officers to help their parolees register to
  vote.
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Does in-person rights restoration prior to parole discharge increase
  post-supervision turnout?
\end{itemize}
\end{frame}

\begin{frame}{Methodology}
\protect\hypertarget{methodology}{}
\begin{itemize}[<+->]
\tightlist
\item
  I limit the pool of individuals to those discharged before the 2018
  registration deadline in 2018. These are all individuals, therefore,
  who could have voted even if the executive order had not been
  implemented.
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  I compare turnout to those treated by the executive order to those who
  were untreated by the order afterwards.
\end{itemize}

\begin{itemize}[<+->]
\tightlist
\item
  Because of ``imperfect compliance'' with the treatment, I adopt an
  instrumental variables approach. Treatment is instrumented by whether
  someone came off parole after the executive order went into effect.
\end{itemize}
\end{frame}

\begin{frame}{Turnout in 2016 Among the Formerly Incarcerated}
\protect\hypertarget{turnout-in-2016-among-the-formerly-incarcerated}{}
\begin{center}\includegraphics[width=0.85\linewidth,height=0.85\textheight]{mpsa_files/figure-beamer/unnamed-chunk-1-1} \end{center}
\end{frame}

\begin{frame}{Turnout in 2018 Among the Formerly Incarcerated}
\protect\hypertarget{turnout-in-2018-among-the-formerly-incarcerated}{}
\begin{center}\includegraphics[width=0.85\linewidth,height=0.85\textheight]{mpsa_files/figure-beamer/unnamed-chunk-2-1} \end{center}
\end{frame}

\begin{frame}{Overall Treatment Effects}
\protect\hypertarget{overall-treatment-effects}{}
\begin{center}\includegraphics[width=0.85\linewidth,height=0.85\textheight]{mpsa_files/figure-beamer/unnamed-chunk-3-1} \end{center}
\end{frame}

\begin{frame}{Treatment Effects Vary by Race}
\protect\hypertarget{treatment-effects-vary-by-race}{}
\begin{center}\includegraphics[width=0.85\linewidth,height=0.85\textheight]{mpsa_files/figure-beamer/unnamed-chunk-4-1} \end{center}
\end{frame}

@@

\begin{frame}[allowframebreaks,allowframebreaks]{References}
\protect\hypertarget{references}{}
\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-Burch2011}{}%
Burch, Traci. 2011. ``Turnout and Party Registration Among Criminal
Offenders in the 2008 General Election.'' \emph{Law \& Society Review}
45 (3): 699--730.
\url{https://doi.org/10.1111/j.1540-5893.2011.00448.x}.

\leavevmode\hypertarget{ref-Burch2012}{}%
---------. 2012. ``Did Disfranchisement Laws Help Elect President Bush?
New Evidence on the Turnout Rates and Candidate Preferences of Florida's
Ex-Felons.'' \emph{Political Behavior} 34 (1): 1--26.
\url{https://doi.org/10.1007/s11109-010-9150-9}.

\leavevmode\hypertarget{ref-Gerber2015}{}%
Gerber, Alan S., Gregory A. Huber, Marc Meredith, Daniel R. Biggers, and
David J. Hendry. 2015. ``Can Incarcerated Felons Be (Re)Integrated into
the Political System? Results from a Field Experiment.'' \emph{American
Journal of Political Science} 59 (4): 912--26.
\url{https://doi.org/10.1111/ajps.12166}.

\leavevmode\hypertarget{ref-Gerber2017}{}%
---------. 2017. ``Does Incarceration Reduce Voting? Evidence About the
Political Consequences of Spending Time in Prison.'' \emph{The Journal
of Politics} 79 (4): 1130--46. \url{https://doi.org/10.1086/692670}.

\leavevmode\hypertarget{ref-Lerman2014}{}%
Lerman, Amy E., and Vesla M. Weaver. 2014. \emph{Arresting Citizenship:
The Democratic Consequences of American Crime Control}. Chicago Studies
in American Politics. Chicago ; London: The University of Chicago Press.

@@

\leavevmode\hypertarget{ref-White2019}{}%
White, Ariel. 2019. ``Misdemeanor Disenfranchisement? The Demobilizing
Effects of Brief Jail Spells on Potential Voters.'' \emph{American
Political Science Review} 113 (2): 311--24.
\url{https://doi.org/10.1017/S000305541800093X}.
\end{cslreferences}
\end{frame}
